\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-21 main.tex
Updates from Overleaf

fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for opt_steps, row in zip(optimesh_steps, axes):
    title = f"optimesh_steps = {opt_steps}"
    for device, ax in zip((ring, square_ring), row):
        # Generate the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        # Visualize the mesh
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
        ax.axis("off")
        ax.set_title(title, fontfamily="monospace")
axes[0, 0].legend(loc="best")
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}

>>>>

fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, opt_steps in zip(axes, optimesh_steps):
    title = f"optimesh_steps = {opt_steps}"
    for ax, device in zip(row, (ring, square_ring)):
        # Generate the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        # Visualize the mesh
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
        ax.axis("off")
        ax.set_title(title, fontfamily="monospace")
axes[0, 0].legend(loc="best")
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}
